Enter our title here

### 2017-08-29 manuscript.tex
edit

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on their laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses and assign a course that they've created for the particular class.

@@

- 'datacamp/testwhat' to help with submission correctness tests

@@

**add an example of a test_function sct

@@

**add example of a normal coding exercise

The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson' 
portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise code and
SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. The simple multiple 
choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises allow instructors to pre
-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises are straightforward to write can 
act as quick checks for understanding throughout the chapter.

**add example of regular multiple choice exercise

>>>>

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses and assign a course that they've created for the particular class.

@@

@@

%add an example of a test_function sct

@@

%add example of a normal coding exercise

The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise 
code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. 
The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
are straightforward to write can act as quick checks for understanding throughout the chapter.

%add example of regular multiple choice exercise
